Arrows for Parallel Computation

### 2018-01-07 paper/content/arxiv/ms.tex
arXiv images

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Varid{parEvalN}\mathbin{::}(\Conid{Trans}\;\Varid{a},\Conid{Trans}\;\Varid{b})\Rightarrow [\mskip1.5mu \Varid{a}\to \Varid{b}\mskip1.5mu]\to [\mskip1.5mu \Varid{a}\mskip1.5mu]\to [\mskip1.5mu \Varid{b}\mskip1.5mu]{}\<[E]%
\\
\>[B]{}\Varid{parEvalN}\mathrel{=}\Varid{spawnF}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
% \begin{figure}[h]
% 	\includegraphics[scale=0.5]{images/parEvalNEden}
% 	\caption{Dataflow of the Eden |parEvalN| version.}
% 	\label{fig:parEvalNEden}
% \end{figure}
% A simplistic graphical depiction of this definition can be found in Fig.~\ref{fig:parEvalNEden}.

@@

\begin{figure}[ht]
	\centering
	\speedupplot{Speedup of distributed \rmtest \enquote{44497 256}}{PArrows Eden}{256}{32}{
	\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
	smooth]{bench-distributed.bench.skelrm-parrows-44497-256.csv};
	}{272}{\plotwidthDist}{272}
	\caption[Speedup distributed Rabin--Miller]{Speedup of the distributed \rmtest benchmark using PArrows with Eden.}
	\label{fig:rabinMillerDistSpeedup}
\end{figure}

@@

\bibitem[\protect\citename{Asada, }2010]{Asada:2010:ASM:1863597.1863607}
Asada, Kazuyuki. (2010).
\newblock Arrows are strong monads.
\newblock {\em Pages  33--42 of:} {\em Proceedings of the Third ACM SIGPLAN
  Workshop on Mathematically Structured Functional Programming}.
\newblock MSFP '10.
\newblock New York, NY, USA: ACM.

@@

\bibitem[\protect\citename{Czaplicki \& Chong,
  }2013]{Czaplicki:2013:AFR:2499370.2462161}
Czaplicki, Evan, \& Chong, Stephen. (2013).
\newblock Asynchronous functional reactive programming for guis.
\newblock {\em Sigplan not.}, {\bf 48}(6), 411--422.

@@

\bibitem[\protect\citename{Foltzer {\em et~al.}\relax,
  }2012]{Foltzer:2012:MPC:2398856.2364562}
Foltzer, Adam, Kulkarni, Abhishek, Swords, Rebecca, Sasidharan, Sajith, Jiang,
  Eric, \& Newton, Ryan. (2012).
\newblock A meta-scheduler for the {Par}-monad: Composable scheduling for the
  heterogeneous cloud.
\newblock {\em Sigplan not.}, {\bf 47}(9), 235--246.

@@

\bibitem[\protect\citename{Harris {\em et~al.}\relax,
  }2005]{Harris:2005:CMT:1065944.1065952}
Harris, Tim, Marlow, Simon, {Peyton Jones}, Simon, \& Herlihy, Maurice. (2005).
\newblock Composable memory transactions.
\newblock {\em Pages  48--60 of:} {\em Proceedings of the 10\xth ACM SIGPLAN
  Symposium on Principles and Practice of Parallel Programming}.
\newblock PPoPP '05.
\newblock ACM.

@@

\bibitem[\protect\citename{Keller {\em et~al.}\relax,
  }2010]{Keller:2010:RSP:1932681.1863582}
Keller, Gabriele, Chakravarty, Manuel~M.T., Leshchinskiy, Roman, {Peyton
  Jones}, Simon, \& Lippmeier, Ben. (2010).
\newblock Regular, shape-polymorphic, parallel arrays in haskell.
\newblock {\em Sigplan not.}, {\bf 45}(9), 261--272.

@@

\bibitem[\protect\citename{Kuper {\em et~al.}\relax,
  }2014]{Kuper:2014:TPE:2666356.2594312}
Kuper, Lindsey, Todd, Aaron, Tobin-Hochstadt, Sam, \& Newton, Ryan~R. (2014).
\newblock Taming the parallel effect zoo: Extensible deterministic parallelism
  with {LVish}.
\newblock {\em Sigplan not.}, {\bf 49}(6), 2--14.

@@

\bibitem[\protect\citename{Liu {\em et~al.}\relax,
  }2009]{Liu:2009:CCA:1631687.1596559}
Liu, Hai, Cheng, Eric, \& Hudak, Paul. (2009).
\newblock Causal commutative arrows and their optimization.
\newblock {\em Sigplan not.}, {\bf 44}(9), 35--46.

@@

\bibitem[\protect\citename{Maier {\em et~al.}\relax,
  }2014]{Maier:2014:HDS:2775050.2633363}
Maier, Patrick, Stewart, Robert, \& Trinder, Phil. (2014).
\newblock The {HdpH} {DSLs} for scalable reliable computation.
\newblock {\em Sigplan not.}, {\bf 49}(12), 65--76.

\bibitem[\protect\citename{Mainland \& Morrisett,
  }2010]{Mainland:2010:NEC:2088456.1863533}
Mainland, Geoffrey, \& Morrisett, Greg. (2010).
\newblock Nikola: Embedding compiled {GPU} functions in {Haskell}.
\newblock {\em Sigplan not.}, {\bf 45}(11), 67--78.

\bibitem[\protect\citename{Marlow {\em et~al.}\relax, }2009]{Marlow2009}
Marlow, S., {Peyton Jones}, S., \& Singh, S. (2009).
\newblock Runtime support for multicore {Haskell}.
\newblock {\em Acm sigplan notices}, {\bf 44}(9), 65--78.

@@

\bibitem[\protect\citename{Marlow {\em et~al.}\relax, }2011]{par-monad}
Marlow, Simon, Newton, Ryan, \& {Peyton Jones}, Simon. (2011).
\newblock A monad for deterministic parallelism.
\newblock {\em Sigplan not.}, {\bf 46}(12), 71--82.

\bibitem[\protect\citename{McDonell {\em et~al.}\relax,
  }2015]{McDonell:2015:TRC:2887747.2804313}
McDonell, Trevor~L., Chakravarty, Manuel M.~T., Grover, Vinod, \& Newton,
  Ryan~R. (2015).
\newblock Type-safe runtime code generation: Accelerate to {LLVM}.
\newblock {\em Sigplan not.}, {\bf 50}(12), 201--212.

\bibitem[\protect\citename{Michael {\em et~al.}\relax,
  }2009]{Michael:2009:IWS:1594835.1504186}
Michael, Maged~M., Vechev, Martin~T., \& Saraswat, Vijay~A. (2009).
\newblock Idempotent work stealing.
\newblock {\em Sigplan not.}, {\bf 44}(4), 45--54.

@@

\bibitem[\protect\citename{Paterson, }2001]{Paterson:2001:NNA:507669.507664}
Paterson, Ross. (2001).
\newblock A new notation for arrows.
\newblock {\em Sigplan not.}, {\bf 36}(10), 229--240.

@@

\bibitem[\protect\citename{Russo {\em et~al.}\relax,
  }2008]{Russo:2008:LLI:1411286.1411289}
Russo, Alejandro, Claessen, Koen, \& Hughes, John. (2008).
\newblock A library for light-weight information-flow security in {Haskell}.
\newblock {\em Pages  13--24 of:} {\em Proceedings of the 1\st ACM SIGPLAN
  Symposium on Haskell}.
\newblock Haskell '08.
\newblock ACM.

@@

\bibitem[\protect\citename{Svensson, }2011]{obsidian-phd}
Svensson, Joel. (2011).
\newblock {\em Obsidian: Gpu kernel programming in haskell}.
\newblock Ph.D. thesis, Chalmers University of Technology.

@@

\bibitem[\protect\citename{van Nieuwpoort {\em et~al.}\relax,
  }2001]{vanNieuwpoort:2001:ELB:568014.379563}
van Nieuwpoort, Rob~V., Kielmann, Thilo, \& Bal, Henri~E. (2001).
\newblock Efficient load balancing for wide-area divide-and-conquer
  applications.
\newblock {\em Sigplan not.}, {\bf 36}(7), 34--43.

>>>>

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Varid{parEvalN}\mathbin{::}(\Conid{Trans}\;\Varid{a},\Conid{Trans}\;\Varid{b})\Rightarrow [\mskip1.5mu \Varid{a}\to \Varid{b}\mskip1.5mu]\to [\mskip1.5mu \Varid{a}\mskip1.5mu]\to [\mskip1.5mu \Varid{b}\mskip1.5mu]{}\<[E]%
\\
\>[B]{}\Varid{parEvalN}\mathrel{=}\Varid{spawnF}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
% \begin{figure}[h]
% 	\includegraphics[scale=0.5]{parEvalNEden}
% 	\caption{Dataflow of the Eden |parEvalN| version.}
% 	\label{fig:parEvalNEden}
% \end{figure}
% A simplistic graphical depiction of this definition can be found in Fig.~\ref{fig:parEvalNEden}.

@@

\begin{figure}[ht]
	\centering
	\speedupplot{Speedup of distributed \rmtest \enquote{44497 256}}{PArrows Eden}{256}{32}{
	\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
	smooth]{\benchmarkDir/distributed-rm/bench-distributed.bench.skelrm-parrows-44497-256.csv};
	}{272}{\plotwidthDist}{272}
	\caption[Speedup distributed Rabin--Miller]{Speedup of the distributed \rmtest benchmark using PArrows with Eden.}
	\label{fig:rabinMillerDistSpeedup}
\end{figure}

@@

\bibitem[\protect\citename{Asada, }2010]{Asada:2010:ASM:1863597.1863607}
Asada, Kazuyuki. (2010).
\newblock Arrows are strong monads.
\newblock {\em Pages  33--42 of:} {\em Proceedings of the Third {ACM SIGPLAN}
  Workshop on Mathematically Structured Functional Programming}.
\newblock MSFP '10.
\newblock New York, NY, USA: ACM.

@@

\bibitem[\protect\citename{Czaplicki \& Chong,
  }2013]{Czaplicki:2013:AFR:2499370.2462161}
Czaplicki, Evan, \& Chong, Stephen. (2013).
\newblock Asynchronous functional reactive programming for guis.
\newblock {\em {SIGPLAN} not.}, {\bf 48}(6), 411--422.

@@

\bibitem[\protect\citename{Foltzer {\em et~al.}\relax,
  }2012]{Foltzer:2012:MPC:2398856.2364562}
Foltzer, Adam, Kulkarni, Abhishek, Swords, Rebecca, Sasidharan, Sajith, Jiang,
  Eric, \& Newton, Ryan. (2012).
\newblock A meta-scheduler for the {Par}-monad: Composable scheduling for the
  heterogeneous cloud.
\newblock {\em {SIGPLAN} not.}, {\bf 47}(9), 235--246.

@@

\bibitem[\protect\citename{Harris {\em et~al.}\relax,
  }2005]{Harris:2005:CMT:1065944.1065952}
Harris, Tim, Marlow, Simon, {Peyton Jones}, Simon, \& Herlihy, Maurice. (2005).
\newblock Composable memory transactions.
\newblock {\em Pages  48--60 of:} {\em Proceedings of the 10\xth {ACM SIGPLAN}
  Symposium on Principles and Practice of Parallel Programming}.
\newblock PPoPP '05.
\newblock ACM.

@@

\bibitem[\protect\citename{Keller {\em et~al.}\relax,
  }2010]{Keller:2010:RSP:1932681.1863582}
Keller, Gabriele, Chakravarty, Manuel~M.T., Leshchinskiy, Roman, {Peyton
  Jones}, Simon, \& Lippmeier, Ben. (2010).
\newblock Regular, shape-polymorphic, parallel arrays in haskell.
\newblock {\em {SIGPLAN} not.}, {\bf 45}(9), 261--272.

@@

\bibitem[\protect\citename{Kuper {\em et~al.}\relax,
  }2014]{Kuper:2014:TPE:2666356.2594312}
Kuper, Lindsey, Todd, Aaron, Tobin-Hochstadt, Sam, \& Newton, Ryan~R. (2014).
\newblock Taming the parallel effect zoo: Extensible deterministic parallelism
  with {LVish}.
\newblock {\em {SIGPLAN} not.}, {\bf 49}(6), 2--14.

@@

\bibitem[\protect\citename{Liu {\em et~al.}\relax,
  }2009]{Liu:2009:CCA:1631687.1596559}
Liu, Hai, Cheng, Eric, \& Hudak, Paul. (2009).
\newblock Causal commutative arrows and their optimization.
\newblock {\em {SIGPLAN} not.}, {\bf 44}(9), 35--46.

@@

\bibitem[\protect\citename{Maier {\em et~al.}\relax,
  }2014]{Maier:2014:HDS:2775050.2633363}
Maier, Patrick, Stewart, Robert, \& Trinder, Phil. (2014).
\newblock The {HdpH} {DSLs} for scalable reliable computation.
\newblock {\em {SIGPLAN} not.}, {\bf 49}(12), 65--76.

\bibitem[\protect\citename{Mainland \& Morrisett,
  }2010]{Mainland:2010:NEC:2088456.1863533}
Mainland, Geoffrey, \& Morrisett, Greg. (2010).
\newblock Nikola: Embedding compiled {GPU} functions in {Haskell}.
\newblock {\em {SIGPLAN} not.}, {\bf 45}(11), 67--78.

\bibitem[\protect\citename{Marlow {\em et~al.}\relax, }2009]{Marlow2009}
Marlow, S., {Peyton Jones}, S., \& Singh, S. (2009).
\newblock Runtime support for multicore {Haskell}.
\newblock {\em {SIGPLAN} not.}, {\bf 44}(9), 65--78.

@@

\bibitem[\protect\citename{Marlow {\em et~al.}\relax, }2011]{par-monad}
Marlow, Simon, Newton, Ryan, \& {Peyton Jones}, Simon. (2011).
\newblock A monad for deterministic parallelism.
\newblock {\em {SIGPLAN} not.}, {\bf 46}(12), 71--82.

\bibitem[\protect\citename{McDonell {\em et~al.}\relax,
  }2015]{McDonell:2015:TRC:2887747.2804313}
McDonell, Trevor~L., Chakravarty, Manuel M.~T., Grover, Vinod, \& Newton,
  Ryan~R. (2015).
\newblock Type-safe runtime code generation: Accelerate to {LLVM}.
\newblock {\em {SIGPLAN} not.}, {\bf 50}(12), 201--212.

\bibitem[\protect\citename{Michael {\em et~al.}\relax,
  }2009]{Michael:2009:IWS:1594835.1504186}
Michael, Maged~M., Vechev, Martin~T., \& Saraswat, Vijay~A. (2009).
\newblock Idempotent work stealing.
\newblock {\em {SIGPLAN} not.}, {\bf 44}(4), 45--54.

@@

\bibitem[\protect\citename{Paterson, }2001]{Paterson:2001:NNA:507669.507664}
Paterson, Ross. (2001).
\newblock A new notation for arrows.
\newblock {\em {SIGPLAN} not.}, {\bf 36}(10), 229--240.

@@

\bibitem[\protect\citename{Russo {\em et~al.}\relax,
  }2008]{Russo:2008:LLI:1411286.1411289}
Russo, Alejandro, Claessen, Koen, \& Hughes, John. (2008).
\newblock A library for light-weight information-flow security in {Haskell}.
\newblock {\em Pages  13--24 of:} {\em Proceedings of the 1\st {ACM SIGPLAN}
  Symposium on {Haskell}}.
\newblock Haskell '08.
\newblock ACM.

@@

\bibitem[\protect\citename{Svensson, }2011]{obsidian-phd}
Svensson, Joel. (2011).
\newblock {\em Obsidian: {GPU} kernel programming in {Haskell}}.
\newblock Ph.D. thesis, Chalmers University of Technology.

@@

\bibitem[\protect\citename{van Nieuwpoort {\em et~al.}\relax,
  }2001]{vanNieuwpoort:2001:ELB:568014.379563}
van Nieuwpoort, Rob~V., Kielmann, Thilo, \& Bal, Henri~E. (2001).
\newblock Efficient load balancing for wide-area divide-and-conquer
  applications.
\newblock {\em {SIGPLAN} not.}, {\bf 36}(7), 34--43.
